---
title: "Visualisation and analysis of probability distributions of variables defined on  spatio-temporal granularities"
type: "meetup"
author: "<br> Sayani Gupta <br> <br> Supervisors: &nbsp; Prof. Rob J Hyndman &nbsp; &nbsp; Prof. Dianne Cook &nbsp; &nbsp; Dr. Peter Toscas"
date: <font size="5"> Department of Econometrics and Business Statistics <br> February 28, 2019
output:
  xaringan::moon_reader:
    css: ["default", "data_viz_theme.css"]
    self_contained: false
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(sugrrants)
library(tsibble)
library(ggridges)
library(viridis)
library(forecast)
library(lubridate)
library(lvplot)
library(gridExtra)
library(tm)
library(SnowballC)
library(wordcloud)
library(readtext)
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE, dev.args=list(bg=grey(0.9), pointsize=8))
```


## <span style="color: DarkBlue"> Visualisation and analysis of probability distributions of variables defined on  spatio-temporal granularities

### <span style="color: Crimson"> Sayani Gupta

.pull-left[


## Motivation 

** Electricity Smart Meter Technology** Meters recording electricity usage (per kWh) every 15 or 30 minutes

**Consumers** to save considerably on their electricity bill 

**Retailers** to reduce costs and increase efficiency

## Data Description

<span style="color: Crimson"> **Type**:<span style="color: Black"> Spatio - Temporal Data
<span style="color: Crimson">**Frequency**:<span style="color: Black"> Half hourly interval meter reading for 14K (approx.)
<span style="color: Crimson">**Time spread**:<span style="color: Black"> 2012 to 2014
<span style="color: Crimson">**Space spread**: <span style="color: Black"> households based in Newcastle, New South Wales, and parts of Sydney
<span style="color: Crimson">**Volume**: <span style="color: Black"> 40 billion half hourly observations

]

.pull-right[

## Exploratory Data Analysis (EDA)

<span style="color: #808000"> Visualization of probability distributions of deconstructed temporal data - effect of time

<span style="color: #4682B4"> Spatio-temporal granularities and probability distribution plots -  effect of time & space

<span style="color: DarkMagenta"> Clustering algorithms for grouping probability distributions on spatio-temporal granularities- finding similar pockets


```{r, echo=FALSE}
wordbase <- readtext("/Users/sgup0008/Documents/ProViz_TimeGrans/_book/thesis_proviz.pdf")
corp <- Corpus(VectorSource(wordbase))
corp <- tm_map(corp, PlainTextDocument)
corp <- tm_map(corp, removePunctuation)
corp <- tm_map(corp, removeNumbers)
corp <- tm_map(corp, tolower)
corp <- tm_map(corp, removeWords, stopwords(kind = "en"))
color <- brewer.pal(8,"Spectral")
wordcloud(corp, max.words = 70, min.freq=15, random.order = FALSE, colors = color)
```
]
